### 2022-11-15 NSF2022/Description/specificaim1v2.tex
...

In the case of granules, bending enters through the splay of the granule
directors. In Figure~\ref{fig:JPv_linearshear}, for example, the
directors have negative, respectively positive, splay $\nabla_{\Sigma}
\cdot \dd$ in the outer, respectively inner monolayers. Here
$\nabla_{\Sigma}\cdot{}$ is the surface divergence. From differential
geometry, we have that $\nabla\cdot \dd = \pm 2H$ whenever $\dd$ is
everywhere normal to $\Sigma$, and this is how curvature enters the
granule-based description. For two-dimensional vesicles, $H$ is replaced
with the curvature $\kappa$ of the curve $\mathcal{C}$. Granules are at
rest when attraction balances repulsion, and will have stretching energy
when the distance between neighboring granules is increased from rest.

>>>>

In the case of granules, bending enters through the splay of the granule
directors. In Figure~\ref{fig:JPv_linearshear}, for example, the
directors have negative, respectively positive, splay $\nabla_{\Sigma}
\cdot \dd$ in the outer, respectively inner monolayers. Here
$\nabla_{\Sigma}\cdot{}$ is the surface divergence. From differential
geometry, we have that $\nabla_{\Sigma} \cdot \dd = \pm 2H$ whenever $\dd$ is
everywhere normal to $\Sigma$, and this is how curvature enters the
granule-based description. For two-dimensional vesicles, $H$ is replaced
with the curvature $\kappa$ of the curve $\mathcal{C}$. Granules are at
rest when attraction balances repulsion, and will have stretching energy
when the distance between neighboring granules is increased from rest.
